%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.5in,right=0.6in,bottom=0.5in]{geometry} 
%\usepackage{tabu}
\usepackage{hyperref}

% Document margins

\name{Parth Lakhani} % Your name

\address{(215) 260 - 8279 \\ \href{mailto:parth@prlakhani.com}{parth@prlakhani.com}}
\address{\url{https://www.linkedin.com/in/prlakhani} \\ \url{https://github.com/prlakhani}}
\begin{document}


%-------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------

\begin{rSection}{Work Experience}
\begin{rSubsection}{Kelsey-Seybold Clinic}{2020 -- Present}{Healthcare Informatics Analyst}{Houston, TX}
\item Use Epic EHR and claims data within SQL Server with Python and PowerBI to inform internal process improvement and decision support initiatives.

\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Komodo Health}{2018 -- 2020}{Data Scientist/Healthcare Analytics Engineer}{Houston, TX/New York, NY}
\item Built data insights team and processes from scratch as first team hire, employing PySpark and Kubernetes.
\item Acted as subject matter expert liaison between client-facing teams and insights team.
\item Used medical/pharmacy claims and lab test data to execute client-facing healthcare analytics projects.

\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Yext}{2016 -- 2017}{Data Strategist}{New York, NY}
\item Working across multiple teams, conducted internal analyses of large customer outcomes datasets to deliver novel insights on best practices, requiring NLP and machine learning techniques.
\item Architected and developed new process automation tools as notebooks or browser-based interfaces.
\item Advised Engineering and Product teams on data governance and data quality initiatives.

\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Captain401}{2015 -- 2016}{Software Developer}{San Francisco, CA}
\item Built client payroll tracking and parsing infrastructure using NodeJS and React
\item Prototyped internal operations tool using Python, Flask, and Postgres
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{UC San Francisco/Massachusetts General Hospital}{2013 -- 2015}{Laboratory Solutions Developer/Research Technician II}{San Francisco, CA/Boston, MA}
\item Independently designed and developed end-to-end ETL and analysis pipeline.
\item Built multiple laboratory inventory and monitoring applications with PaaS/on-premise hosting as needed.
\item Designed novel assays for custom MATLAB and Arduino-based rapid behavioral phenotyping platform.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Mount Sinai School of Medicine, Department of Nephrology}{2010 -- 2013}{Associate Researcher}{New York, NY}
\item Managed team of 3 technicians to run multi-facility mouse colony of 1000+ mice.
\item Studied autoimmunity/alloimmunity connection, including publishing independent research project.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%-------------------------------------------------

%-------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------

\begin{rSection}{Skills}
\vspace{0.3em}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{2.6ex}} p{85ex} }
Languages & Python, SQL, JavaScript, MATLAB, \texttt{bash} scripting, \LaTeX, R, Go
\vspace{0.4em}\\
Technologies & pandas, PySpark, Kubernetes, AWS, Snowflake, scikit-learn, Flask/Django, PostgreSQL/MySQL/SQL Server, PowerBI, Tableau, git, NodeJS, D3, Heroku
\end{tabular}

\end{rSection}

%-------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------

\begin{rSection}{Education}
\vspace{0.3em}

{\bf DataCamp/Coursera/Udacity, }{\em Independent study} \hfill 2015 -- Present \\ 
{\em Coursework in}: data analysis, statistics, data visualization, web development, health informatics

{\bf Swarthmore College, }{\em B.A., Biology } \hfill 2006 -- 2010 \\
{\em Relevant coursework}: Algorithmic Problem Solving, Data Analysis and Visualization, Privacy and Security
\end{rSection}



%\begin{rSection}{Projects}
%\vspace{0.4em}
%\begin{list}{$\diamond$}{\leftmargin=1em}
%\itemsep -0.5em
%\item \textbf{Phenotype database} \textit{(UCSF)}: Wrote \textbf{Python} scripts to process \textbf{MATLAB}-generated data to load into \textbf{Heroku}-hosted \textbf{PostgreSQL} database, and built \textbf{Django} application with \textbf{Bootstrap} front-end to access data and perform routine analyses using server-side \textbf{Python} code.
%\item \href{https://github.com/prlakhani/udacity_swissTournament}{\textbf{Swiss-style tournament database}} \textit{(Udacity)}: Designed a \textbf{Postgres} database to record and manage players, matches, and tournaments, and wrote \textbf{Python} wrapper functions for \textbf{CRUD} \textbf{SQL} queries.
%\item \textbf{Publication: Effects of preexisting autoimmunity on heart graft prolongation after donor-specific transfusion and anti-CD154} \textit{(Mount Sinai)}: Independent research project

%\end{list}
%\end{rSection}


%-------------------------------------------------------------------------
%	EXTRAS SECTION
%-------------------------------------------------------------------------

%\begin{rSection}{Activities and Interests}
%\vspace{0.3em}
%Avid cyclist, homebrewer
%\end{rSection}

%-------------------------------------------------------------------------
%	LANGUAGES SECTION
%-------------------------------------------------------------------------

%\begin{rSection}{Languages}
%\vspace{0.3em}
%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1.5ex}} p{85ex} }
%Native & English (US) \\
%Proficient & Gujarati, Hindi \\
%Conversational & Spanish \\
%\end{tabular}
%
%\end{rSection}


%-------------------------------------------------------------------------
%	EXAMPLE SECTION
%-------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%-------------------------------------------------------------------------


\end{document}
